Illuminating a Dark Lens : A Type Ia Supernova Magnified by \\ the Frontier Fields Galaxy Cluster Abell 2744

### 2015-08-10 APJ.submitted/snTomas.tex
Small corrections noted by SWJ

\noindent The inferred magnifications for the two different fitters are
reported in the final column of Table~\ref{tab:MeasuredMagnification}.
Although we have chosen to use a cosmology-independent approach to
determine the magnifications, we note that these results are fully
consistent with the values that would be determined by comparing the
observed SN \tomas\ distance modulus against the predicted value from
a flat \LCDM\ cosmology. Adopting the cosmological parameters used
in \P14\ and derived in \citet{Sullivan:2011}
(\Ho=71.6, \Om=0.27, \OL=0.73) would give a predicted distance modulus
$dm_{\Lambda CDM}=44.90$ and a measured magnification $\mu=1.9$.
Substituting alternative cosmological
parameters \citep[e.g.,][]{Betoule:2014,Planck:2015} would not
significantly change the inferred magnification or affect our
conclusions.

@@

\smallskip
\change{{\it (2) Strong vs. Strong+Weak':}}
\change{Thirteen of the mass models evaluated here are constrained only using
strong-lensing features such as multiply-imaged background galaxies
and highly magnified arcs.  There are now $\sim$150 known lensed
images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
located several arcseconds outside the core region of the cluster
where these multiply-imaged galaxies are found.  Therefore these
``strong-lensing only'' models must necessarily rely on extrapolations
to provide a prediction for the SN \tomas\ magnification.}

@@

This work is dedicated to our colleague and friend Tomas Dahlen, for
whom this supernova has been named in memorium. He is dearly missed.

>>>>

\noindent The inferred magnifications for the two different fitters are
reported in the final column of Table~\ref{tab:MeasuredMagnification}.
Although we have chosen to use a cosmology-independent approach to
determine the magnifications, we note that these results are fully
consistent with the values that would be determined by comparing the
observed SN \tomas\ distance modulus against the predicted value from
a flat \LCDM\ cosmology. Adopting the cosmological parameters used
in \P14\ and derived in \citet{Sullivan:2011}
(\Ho=71.6, \Om=0.27, \OL=0.73) would give a predicted distance modulus
${\rm dm}_{\Lambda CDM}=44.90$ and a measured magnification $\mu=1.9$.
Substituting alternative cosmological
parameters \citep[e.g.,][]{Betoule:2014,Planck:2015} would not
significantly change the inferred magnification or affect our
conclusions.

@@

\smallskip
\change{{\it (2) Strong vs. Strong+Weak:}}
\change{Thirteen of the mass models evaluated here are constrained only using
strong-lensing features such as multiply-imaged background galaxies
and highly magnified arcs.  There are now $\sim$150 known lensed
images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
located several arcseconds outside the core region of the cluster
where these multiply-imaged galaxies are found.  Therefore these
``strong-lensing only'' models must necessarily rely on extrapolations
to provide a prediction for the SN \tomas\ magnification.}

@@

This work is dedicated to our colleague and friend Tomas Dahlen, for
whom this supernova has been named in memoriam. He is dearly missed.
